On Star Formation at Dynamical Resonances of the Bar

### 2020-07-07 paper/ms.tex
Add areport macro
Update ICs part of text

\newcommand{\arepo}{\textsc{Arepo}}
\newcommand{\smuggle}{\textsc{SMUGGLE}}

@@

\section{Introduction}
Introduction.

@@

>>>>

\newcommand{\arepo}{\textsc{Arepo}}
\newcommand{\areport}{\textsc{Arepo-RT}}
\newcommand{\smuggle}{\textsc{SMUGGLE}}

@@

\section{Introduction}
Roughly two-thirds of spiral galaxies are known to host bars in the
near-infrared, about half of which are strong
\citep[e.g.][]{2000AJ....119..536E}.

@@

\subsection{Initial Conditions}
The starting point for the construction of our initial conditions is the
N-body model GALAKOS \citep{2020ApJ...890..117D}. GALAKOS has structural
parameters and a circular velocity curve which are in reasonable agreement
with current data. However, GALAKOS is a particularly good starting point
because as \citet{2020ApJ...890..117D} showed, the disk forms a strong bar
after ~ 1 Gyr. The bar then grows, until at ~ 2.5 Gyr it has grown and slowed
down to a pattern speed of ~40 km/s/kpc. Evidence is mounting that the Milky
Way's bar is long and slow, just like that in GALAKOS.

We convert a fraction (10\%) of the initial stellar disk of GALAKOS to a gas
disk. As described in \citet{2005MNRAS.361..776S}, the gas disk is initially
in hydrostatic equilibrium. We assumed an ideal EOS for the gas phase,
consistent with our underlying physical model. We make two further
modifications to this setup. First, we ``core'' the gas profile -- instead of
assuming the gas surface density profile is exponential, we assume it is a
constant value within some radius $R_{\text{core}}$. Specifically,
\beq
\Sigma_{\text{gas}} = \Sigma_{0,\text{gas}} \times \begin{cases} 
      e^{-R_{\text{core}}/H} & R \leq R_{\text{core}} \\
      e^{-R/H} & R > R_{\text{core}}\text{,}
   \end{cases}
\eeq
where $H$ is the scale length of the disk and $\Sigma_{0,\text{gas}} =
\frac{M_{\text{gas}}}{2\pi H^2}$ is the central surface density. When
$R_{\text{core}}/H=1$ and $1.4$, $\sim10\%$ and $\sim20\%$ of the gas disk
mass is removed, respectively. This mass is not returned to another component
and is thus removed from the initial conditions entirely. However, since our
assumed gas fraction is $10\%$, this only represents a total reduction in the
disk mass by a few percent. The surface density profile of the stellar disk is
unchanged, though its velocity distribution is suitably altered.

The second modification we make is to treat the initial disk particles as star
particles. In, e.g., \citet{2019MNRAS.489.4233M} the initial disk is assumed
to be a purely collisionless component with no feedback contributions.
Instead, we assume the initial disk particles are star particles so they may
contribute gas through AGB channels. This requires assigning an age and
metallicity to each star particle. We randomly draw the age and metallicity of
each star according to the age-metallicity-radius relation of
\citet{2018ApJ...865...96F}. This ignores vertical variations which is
implemented in other models \citep[e.g.][]{2020arXiv200503646S}.

Our goal is now to construct an initial disk galaxy with gas that, like
GALAKOS, forms a strong bar. The underlying method GALAKOS uses (namely
MakeNewDisk) can already convert a fraction of the initial stellar disk to a
gas disk which is initially in hydrostatic equilibrium. However, if this setup
is naive
